\begin{problem}{C: Snek}

Jastion likes playing the raddest games, like slither.io and agar.io.
He's a bit of a hipster though, so he likes doing things before they are cool.
He realizes that if he makes his own spin-off of one of these games that he'll definitely be playing it before it is cool.

Jastion decides to make a game called snek.io, where a bunch of sneks roam around and eat each other to get bigger.
He made some pretty bad decisions with the game and it's not very fun.
First, a snek can only eat the snek closest to its size and larger than it.
Sneks grow each time they eat another snek, but the amount they grow is constant so it does not matter how big the sneks they eat are.

All of the other players' sneks start out at various sizes, but Jastion's snek always starts at size $0$ (it's very small!).
This means that the first snek the Jastion may eat must be the next smallest one.
Once that snek is eaten and Jastion's snek grows, he must then eat the next snek that is larger than him and closest to its size.
He will continue to do this until he is the largest snek.

Because of Jastion's odd choices with this game, none of the other players can figure out how to eat the other sneks.
Jastion is the only one who understands the rules properly, therefore his snek is the only one that will eat other sneks.

Jastion wants your help.
Given a list of the sizes of the other sneks' sizes, and the amount Jastion's snek will grow each time he eats a snek, he wants you to tell him which sneks may he eat in the order he may eat them.
\end{problem}

\begin{formalin}
The first line contains two integers. The first, $n$ ($1 \leq n \leq 10^5$), is the amount of sneks other than Jastion's in the game.
The second, $m$ ($1 \leq m \leq 10^5$), is the amount that Jastion's snek will grow after each snek he eats.

The second line contains integers $s$ ($1 \leq s \leq 10^9$) from $s_1$ to $s_n$, the $i$th of which corresponds to the size of the snek in the $i$th position.
\end{formalin}

\begin{formalout}
On a single line, output the positions of the sneks that Jastion's snek may eat in the order he may eat them.
\end{formalout}

\begin{datain}
10 1
1 2 3 4 5 6 7 8 9 10
\end{datain}
\begin{dataout}
1 2 3 4 5 6 7 8 9 10
\end{dataout}

\begin{datain}
10 2
1 2 3 4 5 6 7 8 9 10
\end{datain}
\begin{dataout}
1 3 5 7 9
\end{dataout}