\begin{problem}{1: Peter Rabbit}
Peter Rabbit, like other rabbits, needs to eat. His favorite food to eat is carrots.
As Peter notices a carrot, he eats the carrot and searches for more carrots.
He can hop up, down, left, and right on safe places of the ground to get to other carrots.
It's very important for Peter Rabbit to avoid rabbit holes in the ground because if he falls into one, he cannot get out.
Help Peter Rabbit collect all the carrots on the map while he avoids falling in any holes and avoids falling off the map.
\end{problem}

\begin{formalin}
The first line contains two integers, $x$ and $y$ ($1 \leq x, y \leq 10$) where $x$ is the length of the map and $y$ is the height of the map.

The next x lines contains y characters. The possible characters are as follows:
\begin{itemize}
\item R - The starting postion of Peter Rabbit
\item G - A safe piece of Ground for Peter Rabbit to hop to
\item H - A Hole that Peter Rabbit must avoid
\item C - A Carrot that Peter Rabbit wants to hop to
\end{itemize}

As Peter Rabbit consumes a Carrot that he lands on, the Carrot C then becomes ground G.
It is known that Peter Rabbit is able to hop to any Carrot meaning no Carrot is isolated on an island.
\end{formalin}

\begin{formalout}
Output any valid sequence of hops up U, down D, left L, and right R so that Peter Rabbit collects all the carrots.
Make sure that Peter Rabbit does not fall off the map and does not fall in a rabbit hole.
The last move Peter Rabbit makes must land on a carrot. Otherwise wrong answer would be given for excessive output.
\end{formalout}

\begin{datain}
1 5
R C C G C
\end{datain}
\begin{dataout}
RRRR
\end{dataout}

\begin{datain}
1 3
C R C
\end{datain}
\begin{dataout}
LRR
\end{dataout}

\begin{datain}
2 5
C C G C C
C H H H R
\end{datain}
\begin{dataout}
ULLLLD
\end{dataout}
